Ground state energy of quantum dots using the coupled cluster method

### 2018-06-06 project_2/article/article.tex
Add results for N = 12 and N = 20

    \begin{table}
        \centering
        \caption{Here we look at $N = 12$ particles ($R = 3$ shells).}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF) \\
                \hline
                      & $3$ & $46.361130$ & $46.361130$ & $46.361130$ \\
                      & $4$ & $43.663266$ & $45.837079$ & $43.309845$ \\
                      & $5$ & $41.108850$ & $45.456882$ & $40.654709$ \\
                      & $6$ & $40.750512$ & \nan & $40.068340$ \\
                $0.5$ & $7$ & $40.302718$ & \nan & $39.508500$ \\
                      & $8$ & $40.263751$ & \nan & $39.399128$ \\
                      & $9$ & $40.216688$ & \nan & $39.329310$ \\
                      & $10$ & $40.216251$ & \nan & $39.309409$ \\
                      & $11$ & $40.216194$ & \nan & $39.296007$ \\
                      & $12$ & $40.216165$ & \nan & $39.285968$ \\
                \hline
                      & $3$ & $73.765549$ & $73.765549$ & $73.765549$ \\
                      & $4$ & $70.673849$ & $73.314476$ & $70.324250$ \\
                      & $5$ & $67.569930$ & $72.990679$ & $67.031096$ \\
                      & $6$ & $67.296869$ & \nan & $66.526677$ \\
                $1.0$ & $7$ & $66.934744$ & \nan & $66.049564$ \\
                      & $8$ & $66.923094$ & \nan & $65.972157$ \\
                      & $9$ & $66.912244$ & \nan & $65.921204$ \\
                      & $10$ & $66.912035$ & \nan & $65.889281$ \\
                      & $11$ & $66.911364$ & \nan & $65.866715$ \\
                      & $12$ & $66.911364$ & \nan & $65.849775$ \\
                \hline
                      & $3$ & $120.722260$ & $120.722260$ & $120.722260$ \\
                      & $4$ & $117.339641$ & $120.299999$ & $116.995036$ \\
                      & $5$ & $113.660396$ & $120.012284$ & $113.048934$ \\
                      & $6$ & $113.484866$ & $119.872007$ & $112.658821$ \\
                $2.0$ & $7$ & $113.247601$ & $119.662201$ & $112.309482$ \\
                      & $8$ & $113.246578$ & $119.584733$ & $112.235521$ \\
                      & $9$ & $113.246302$ & $119.524417$ & $112.181828$ \\
                      & $10$ & $113.245854$ & $119.472283$ & $112.140661$ \\
                      & $11$ & $113.245255$ & $119.430435$ & $112.109972$ \\
                      & $12$ & $113.245183$ & $119.394712$ & $112.085683$
            \end{tabular}
        \end{ruledtabular}
        \label{tab:N12}        
    \end{table}

    \begin{table}
        \centering
        \caption{N = 20}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF)

            \end{tabular}
        \end{ruledtabular}
        \label{tab:N20}        
    \end{table}

>>>>

    \begin{table}
        \centering
        \caption{Here we look at $N = 12$ particles ($R = 3$ shells).  We did
        not achieve convergence using the harmonic oscillator basis for the
        lower frequency values and large number of shells.}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF) \\
                \hline
                      & $3$ & $46.361130$ & $46.361130$ & $46.361130$ \\
                      & $4$ & $43.663266$ & $45.837079$ & $43.309845$ \\
                      & $5$ & $41.108850$ & $45.456882$ & $40.654709$ \\
                      & $6$ & $40.750512$ & \nan & $40.068340$ \\
                $0.5$ & $7$ & $40.302718$ & \nan & $39.508500$ \\
                      & $8$ & $40.263751$ & \nan & $39.399128$ \\
                      & $9$ & $40.216688$ & \nan & $39.329310$ \\
                      & $10$ & $40.216251$ & \nan & $39.309409$ \\
                      & $11$ & $40.216194$ & \nan & $39.296007$ \\
                      & $12$ & $40.216165$ & \nan & $39.285968$ \\
                \hline
                      & $3$ & $73.765549$ & $73.765549$ & $73.765549$ \\
                      & $4$ & $70.673849$ & $73.314476$ & $70.324250$ \\
                      & $5$ & $67.569930$ & $72.990679$ & $67.031096$ \\
                      & $6$ & $67.296869$ & \nan & $66.526677$ \\
                $1.0$ & $7$ & $66.934744$ & \nan & $66.049564$ \\
                      & $8$ & $66.923094$ & \nan & $65.972157$ \\
                      & $9$ & $66.912244$ & \nan & $65.921204$ \\
                      & $10$ & $66.912035$ & \nan & $65.889281$ \\
                      & $11$ & $66.911364$ & \nan & $65.866715$ \\
                      & $12$ & $66.911364$ & \nan & $65.849775$ \\
                \hline
                      & $3$ & $120.722260$ & $120.722260$ & $120.722260$ \\
                      & $4$ & $117.339641$ & $120.299999$ & $116.995036$ \\
                      & $5$ & $113.660396$ & $120.012284$ & $113.048934$ \\
                      & $6$ & $113.484866$ & $119.872007$ & $112.658821$ \\
                $2.0$ & $7$ & $113.247601$ & $119.662201$ & $112.309482$ \\
                      & $8$ & $113.246578$ & $119.584733$ & $112.235521$ \\
                      & $9$ & $113.246302$ & $119.524417$ & $112.181828$ \\
                      & $10$ & $113.245854$ & $119.472283$ & $112.140661$ \\
                      & $11$ & $113.245255$ & $119.430435$ & $112.109972$ \\
                      & $12$ & $113.245183$ & $119.394712$ & $112.085683$ \\
                \hline
                $5.0$ & $3$ & $242.334878$ & $242.334878$ & $242.334878$ \\
                      & $4$ & $238.739590$ & $241.927593$ & $238.394598$ \\
                      & $5$ & $234.352741$ & $241.663950$ & $233.680649$ \\
                      & $6$ & $234.282331$ & $241.507595$ & $233.425243$ \\
                      & $7$ & $234.194820$ & $241.390524$ & $233.226529$ \\
                      & $8$ & $234.194058$ & $241.293416$ & $233.137932$ \\
                      & $9$ & $234.190796$ & $241.221056$ & $233.070206$ \\
                      & $10$ & $234.190714$ & $241.158896$ & $233.020009$ \\
                      & $11$ & $234.190665$ & $241.109926$ & $232.980634$ \\
                      & $12$ & $234.190552$ & $241.068091$ & $232.948528$
            \end{tabular}
        \end{ruledtabular}
        \label{tab:N12}        
    \end{table}

    \begin{table}
        \centering
        \caption{In this table we look at $N = 20$ particles ($R = 4$ shells).
        We did not achieve convergence using the harmonic oscillator basis for
        the lower frequency values and large number of shells.}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF) \\
                \hline
                $1.0$ & $4$ & $177.963297$ & $177.963297$ & $177.963297$ \\
                      & $5$ & $168.792442$ & $177.206535$ & $168.459124$ \\
                      & $6$ & $161.339720$ & \nan & $160.594507$ \\
                      & $7$ & $159.958722$ & \nan & $158.841119$ \\
                      & $8$ & $158.400172$ & \nan & $157.038330$ \\
                      & $9$ & $158.226030$ & \nan & $156.676039$ \\
                      & $10$ & $158.017666$ & \nan & $156.367930$ \\
                      & $11$ & $158.010276$ & \nan & $156.292422$ \\
                      & $12$ & $158.004951$ & \nan & $156.238258$ \\
                \hline
                $2.0$ & $4$ & $286.825295$ & $286.825295$ & $286.825295$ \\
                      & $5$ & $276.898195$ & $286.159165$ & $276.381708$ \\
                      & $6$ & $267.269712$ & $266.413122$ & $285.614965$ \\
                      & $7$ & $266.213200$ & \nan & $264.969415$ \\
                      & $8$ & $264.933621$ & \nan & $263.434546$ \\
                      & $9$ & $264.874009$ & \nan & $263.215451$ \\
                      & $10$ & $264.809953$ & \nan & $263.046184$ \\
                      & $11$ & $264.809900$ & \nan & $262.963702$ \\
                      & $12$ & $264.809306$ & \nan & $262.899697$ \\
                \hline
                $5.0$ & $4$ & $563.773951$ & $563.773951$ & $563.773951$ \\
                      & $5$ & $552.630093$ & $563.160136$ & $552.118708$ \\
                      & $6$ & $540.804719$ & $562.692231$ & $539.824400$ \\
                      & $7$ & $540.227792$ & $562.306124$ & $538.886073$ \\
                      & $8$ & $539.499326$ & $562.114280$ & $537.925127$ \\
                      & $9$ & $539.495940$ & \nan & $537.769045$ \\
                      & $10$ & $539.494611$ & \nan & $537.646667$ \\
                      & $11$ & $539.493512$ & \nan & $537.548827$ \\
                      & $12$ & $539.491764$ & \nan & $537.470616$ \\
                \hline
                $10.0$ & $4$ & $973.032700$ & $973.032700$ & $973.032700$ \\
                       & $5$ & $961.371081$ & $972.439477$ & $960.862053$ \\
                       & $6$ & $948.057077$ & $972.002302$ & $947.019789$ \\
                       & $7$ & $947.765473$ & $971.716015$ & $946.399546$ \\
                       & $8$ & $947.410304$ & $971.508583$ & $945.827806$ \\
                       & $9$ & $947.409439$ & $971.332132$ & $945.663819$ \\
                       & $10$ & $947.404929$ & $971.193592$ & $945.528489$ \\
                       & $11$ & $947.404360$ & $971.076617$ & $945.424174$ \\
                       & $12$ & $947.403875$ & $970.978571$ & $945.339079$ \\
            \end{tabular}
        \end{ruledtabular}
        \label{tab:N20}        
    \end{table}
